Spin canonical divisors of log stacky curves

### 2015-06-21 stacky_write_up/spin_cring.tex
Moved lemma from section 4 to section 3 and made it more general

\usepackage{tikz}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

@@

We will prove this by induction using methods analogous to ones of VZB\todo{add 
reference}.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D
\sim \frac{\alpha}{\beta} P$:
\begin{lem}\label{lem:O'Dorney_1_point}
Let 
\[
	0<\frac{c_1}{d_1}<\frac{c_2}{d_2}<...<\frac{c_r}{d_r}=\frac{\alpha}{\beta}
\] 
be the nonnegative best lower approximation\todo{define this above} of $\frac{\alpha}{\beta}
$.  Then $R_D$ is generated up to degree $\beta$ by generators $y_1,...,y_r$ where $y_i$ 
lies in degree $d_i$ with pole of degree $c_i$ at $P$.  
\end{lem}
\begin{proof}
See O'Dorney \todo{provide reference}.
\end{proof}

The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 
8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.

@@

\todo{Extend Lemma \ref{lem:minimal:quadratic} to commutative diagrams to show minimality}
\end{proof}

@@

\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
rings with kernel $I,$ such that $I$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}

\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]

\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

@@

\begin{enumerate}
	\item[(a)] $(\deg \lfloor e_3 \rfloor, \max_{d \geq 0} \# S_{(
		\sigma_1, J_1)}(3)) = (1, 0)$

	\item[(b)] $(\deg \lfloor e_2 \rfloor, \max_{d \geq 0} \#S_{(
		\sigma_2, J_2)}(2)) = (1, 0)$ \\
		$(\deg \lfloor e_3 \rfloor, \max_{d \geq 0} \#S_{(\sigma_2, J_2)}(3))
		= (1, 0)$

	\item[(c)] $(\deg \lfloor e_1 \rfloor, \max_{d \geq 0}
		\#S_{(\sigma_3, J_3)}(1)) = (2, 1)$ \\
		$(\deg \lfloor e_2 \rfloor, \max_{d \geq 0}
		\#S_{(\sigma_3, J_3)}(2)) = (2, 1)$ \\
		$(\deg \lfloor e_3 \rfloor, \max_{d \geq 0}
		\#S_{(\sigma_3, J_3)}(3)) = (1, 0)$

	\item[(d)] $(\deg \lfloor e_i \rfloor, \max_{d \geq 0}
		\#S_{(\sigma_4, J_4)}(i)) = (3, 1)$	for $i \neq 4$ \\
		$(\deg \lfloor e_4 \rfloor, \max_{d \geq 0} \#S_{(\sigma_4, J_4)}(4))
		= (2, 0)$.

	\item[(e)] $(\deg \lfloor e_i \rfloor, \max_{d \geq 0}
		\#S_{(\sigma_5, J_5)}(1)) = (5, 0)$	for all $i \in J$.
\end{enumerate}

>>>>

\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

@@

First we prove a nice result about minimal generation of ideals of relations:

\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
generated in degree 1 that are equipped with monomial ordering $\prec$.
 Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
\[
	\begin{tikzcd}
	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
Further suppose that $I'$ is generated over $I$ by elements $f_1,
\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_ix_j, y_iy_j\}$ and no monomial of $f_i$
is of the form $y_i$.  Then, the elements $f_i$ determine minimal
generators for $I'$ over $I$.
\end{lem}

\begin{proof}
Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
\]
\[
	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
\]

\noindent
determines map of rings, no longer necessarily graded. 
By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent.  By the theory of Grobner basis,
\[
	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
\]
so
\[
	\dim_k (I'/I)_2=j.
\]
This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}
\begin{rem}\label{rem:minimal_quadratic_trivial_case}
It will be useful to use lemma \ref{lem:minimal_quadratic} in the case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$ are $k$-minimal generators for $I'$ (over the trivial base vector space).  
\end{rem}

We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
reference} and O'Dorney\todo{reference}.

@@

In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
\todo{What about $\frac{\alpha}{beta}>1$?}
\end{proof}

@@

@@

\begin{enumerate}
	\item[(a)] $(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0} \# S_{(
		\sigma_1, J_1)}(3)) = (1, 0)$

	\item[(b)] $(\deg \lfloor e_2 L \rfloor, \max_{d \geq 0} \#S_{(
		\sigma_2, J_2)}(2)) = (1, 0)$ \\
		$(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0} \#S_{(\sigma_2, J_2)}(3))
		= (1, 0)$

	\item[(c)] $(\deg \lfloor e_1 L \rfloor, \max_{d \geq 0}
		\#S_{(\sigma_3, J_3)}(1)) = (2, 1)$ \\
		$(\deg \lfloor e_2 L \rfloor, \max_{d \geq 0}
		\#S_{(\sigma_3, J_3)}(2)) = (2, 1)$ \\
		$(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0}
		\#S_{(\sigma_3, J_3)}(3)) = (1, 0)$

	\item[(d)] $(\deg \lfloor e_i  L \rfloor, \max_{d \geq 0}
		\#S_{(\sigma_4, J_4)}(i)) = (3, 1)$	for $i \neq 4$ \\
		$(\deg \lfloor e_4 L \rfloor, \max_{d \geq 0} \#S_{(\sigma_4, J_4)}(4))
		= (2, 0)$.

	\item[(e)] $(\deg \lfloor e_i L \rfloor, \max_{d \geq 0}
		\#S_{(\sigma_5, J_5)}(1)) = (5, 0)$	for all $i \in J$.
\end{enumerate}
